Placeholder title: Formal methods in constraint-based learning

### 2024-01-09 ITP draft/draft_lipics.tex

Complexity increase depending on DL is. While "complexity" is not easy to measure for a DL on paper it is obvious in its impact in formalisation. Associativity of conjunction for Łukawsiewicz, Godel and product all have around 10 lines (get exact after cleanup) - but Yager takes 38 (again, correct after cleanup). If I prove STL mention that (if case split in analogous ways to other proofs we get 38 cases)

@@

\section{Placeholder title: stl example}

>>>>

Complexity increase depending on DL is. While ``complexity'' is not easy to measure for a DL on paper it is obvious in its impact in formalisation. Associativity of conjunction for Łukawsiewic, Godel and product all have around 10 lines (get exact after cleanup) - but Yager takes 38 (again, correct after cleanup). If I prove STL mention that (if case split in analogous ways to other proofs we get 38 cases)

@@

\section{Shadow lifting, idempotence and associativity}

The claim that shadow lifting and associativity cannot hold together is inaccurate, we need idempotence too.

To make this formal, let us assume a generic semantic interpretation of and (f), with the following properties.

[[ p /\ q ]] = f [[ p ]]  [[ q ]] (it's structural)

I: [[p /\ p]] = [[p]] (has idempotence)

A: [[p /\ (q /\ r)]] = [[(p /\ q) /\ r]] (has associativity)

(has shadow lifting)
SL1: d [[p /\ q]] / d p > 0
SL2: d [[p /\ q]] / d q > 0

[[ 1 /\ (1 /\ 1.1) ]] =? [[ 1 /\ (1.1 /\ 1.1) ]]

[[ 1 /\ (1 /\ 1.1) ]] =A [[ (1 /\ 1) /\ 1.1 ]] =I [[ 1 /\ 1.1 ]] =I [[ 1 /\ (1.1 /\ 1.1) ]]

[[ 1 /\ 1.1 ]] <SL1 [[ 1.1 /\ 1.1 ]]
->
[[ 1 /\ (1 /\ 1.1) ]] <SL2 [[ 1 /\ (1.1 /\ 1.1) ]]
